SLE martingales in coset conformal field theory

### 2012-04-13 AffineLieAlgebras/SLE/paper.tex
Some changes in wording in introduction. Acknowledgments added.

\abstract{
  The problem is to provide a way for the concurrent use of Scramm-Loewner evolution (SLE) and conformal field theory (CFT). Both SLE and CFT are popular instruments to study critical behavior of physical models in two dimensions, but they use different objects. While Scharmm-Loewner evolution has natural connection with lattice models and is suitable for strict proofs, it lacks computational and predictive power of conformal field theory. In order to connect two approaches we consider CFT correlation functions which are martingales with respect to SLE. We establish necessary and sufficient conditions on such observables for coset models of conformal field theory and Schramm-Loewner evolution on group manifolds and check the consistency with the  behaviour of parafermionic models.}

@@

SLE describes critical behavior. It is convenient for strict mathematical proofs. For many lattice models  the convergence of  domain walls to SLE was proved.

@@

>>>>

\abstract{
  In order to provide a way for the concurrent use of Schramm-Loewner evolution (SLE) and conformal field theory (CFT) we consider CFT correlation functions which are martingales with respect to SLE.  We establish necessary and sufficient conditions on such observables for coset models of conformal field theory and Schramm-Loewner evolution on group manifolds and check the consistency with the  behaviour of parafermionic models. Both SLE and CFT are popular instruments to study critical behavior of physical models in two dimensions, but they use different objects. While Scharmm-Loewner evolution has natural connection with lattice models and is suitable for strict proofs, it lacks computational and predictive power of conformal field theory.}

@@

Schramm-Loewner evolution \cite{schramm2000scaling} is a stochastic process used to study critical behavior \cite{Cardy:2005kh,rohde2005basic}. For many lattice models  the convergence of  domain walls to SLE traces was proved \cite{bauer20062d,schramm2006conformally}.

@@

\section*{Acknowledgements}
\label{sec:acknowledgements}
 I am grateful to A. Bytsko, K. Izyurov, D. Chelkak and R. Santachiara for the discussions on SLE and WZNW models. This work  is supported by
the Chebyshev Laboratory (Department of Mathematics and Mechanics,
Saint-Petersburg State University) under the grant 11.G34.31.0026
of the Government of the Russian Federation.
